### 2020-03-26 Common/chapters/transfer_learning.tex
Julien and Johan: minor

\section{Transfer learning implementation}
\subsection{Layer freezing}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}After each dataset switch, the model is first trained with freezed layers. The freezed layers are those considered as feature extractor, i.e. the first layers of the model. The exact point where the model is split is right after the convolutions. To perform this freezing, multiple steps are required:
\begin{enumerate}
	\item Reset the last layers. To achieve this, an instance of the model is created by loading the state dictionary of the previous one, before replacing the module containing the last layers with a new instance (i.e. a new initialization). 
	\item Iterate over the batch normalization layers and freeze them. Step 3 is not sufficient to freeze batch normalization layers. In an implementation based on PyTorch, this can be achieved by calling \textit{module.eval()} on each module containing such layers (after the \textit{model.train()} call). 
	\item Only pass the parameters of these last layers to the optimizer.
\end{enumerate}

@@

Then, after each epoch of every other transfer learning step, the saved decision maker is attached to the current feature extractor. This temporary model is then tested on the target training and validation sets, which results in different training and validation metrics.

>>>>

\section{Transfer learning implementation}
\subsection{Layer freezing}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}After each dataset switch, the model is first trained with frozen layers. The frozen layers are those considered as feature extractor, i.e. the first layers of the model. The exact point where the model is split is right after the convolutions. To perform this freezing, multiple steps are required:
\begin{enumerate}
	\item Reset the last layers. To achieve this, an instance of the model is created by loading the state dictionary of the previous one, before replacing the module containing the last layers with a new instance (i.e. a new initialization). 
	\item Iterate over the batch normalization layers and freeze them. Step 3 is not sufficient to freeze batch normalization layers. In an implementation based on PyTorch, this can be achieved by calling \textit{module.eval()} on each module containing such layers (after the \textit{model.train()} call). 
	\item Only pass the parameters of these last layers to the optimizer.
\end{enumerate}

@@

Then, after each epoch of every other transfer learning step, the saved decision maker is attached to the current feature extractor. This temporary model is then tested on the target validation set, which results in different validation metrics that summarize the whole process.
